Parameter Space Representation of Pareto Front to Explore Hardware-Software Dependencies

### 2015-01-26 introduction.tex
AA: rilettura fatta e colpo di aspell

\section{Related work and Our Contribution}
\secL{Related-work}
Many different design space exploration algorithms have been proposed
in literature. Exploring the design space of embedded systems is a difficult not only because of the huge size of the parameter space, but also due to the tight \emph{dependencies} (see~\defR{dependency}) between parameters, which impact the objectives.
Due to this complexity, exploration algorithms are usually heuristic and, to a large extent, rely on simple intuitions rather then formal arguments.

>>>>

\section{Related work and Our Contribution}
\secL{Related-work}
Many different design space exploration algorithms have been proposed
in literature. Exploring the design space of embedded systems is difficult not only because of the huge size of the parameter space, but also due to the tight \emph{dependencies} between parameters, which impact the objectives.
Due to this complexity, exploration algorithms are usually heuristic and, to a large extent, rely on simple intuitions rather then formal arguments.

### 2015-01-26 paper.tex
AA: rilettura fatta e colpo di aspell

\title{Parameter Space Representation of Pareto Front to
Explore Hardware-Software Dependencies}
\author{VINCENZO CATANIA
\affil{University of Catania}
ANDREA ARALDO
\affil{Universit\'e Paris-Sud and T\'el\'ecom ParisTech, France}
DAVIDE PATTI
\affil{University of Catania}
}

@@

\begin{bottomstuff}
Author's addresses: V. Catania, DIEEI University of Catania;
A. Araldo, Universit\'e Paris-Sud and T\'el\'ecom ParisTech, France;
D. Patti, DIEEI University of Catania.
\end{bottomstuff}

@@

\section{Conclusions}
\secL{Conclusions}
In this work we presented PS, a multi-objective strategy which 
introduces the concept of Parameter Space representation of Pareto
Front. A case study of a VLIW architecture involving strong
hardware/software dependencies has been analyzed to evaluate
effectiveness with different amount of simulations budget.
A qualitative/quantitative comparison against a widespread multi-objective genetic
approach showed how the proposed strategy can result in a different
distribution of Pareto points which trades solutions granularity with
improved Pareto extension.

>>>>

\title{Parameter Space Representation of Pareto Front to
Explore Hardware-Software Dependencies}
\author{VINCENZO CATANIA
\affil{University of Catania}
ANDREA ARALDO
\affil{Universit\'e Paris-Sud and T\'el\'ecom ParisTech}
DAVIDE PATTI
\affil{University of Catania}
}

@@

\begin{bottomstuff}
Author's addresses: V. Catania, DIEEI University of Catania;
A. Araldo, Universit\'e Paris-Sud and T\'el\'ecom ParisTech;
D. Patti, DIEEI University of Catania.
\end{bottomstuff}

@@

\section{Conclusions}
\secL{Conclusions}
In this work we presented PS, a multi-objective strategy which 
introduces the concept of Parameter Space representation of Pareto
Front. A case study of a VLIW architecture involving strong
hardware/software dependencies has been analyzed to evaluate
the PS effectiveness with different amounts of simulations budget.
A qualitative/quantitative comparison against a widespread multi-objective genetic
approach showed that the proposed strategy can result in a different
distribution of Pareto points which balances solutions granularity and
improved Pareto extension.
